True versus apparent shapes of astrophysical bow shocks

### 2017-01-30 papers/Paper1/sec-conic.tex
Update some references in appendix
Figure 5 is now in one column
Finish improvements to Fig 5

%Instead of the excentricity, we utilize the parameter $\theta_c$ to characterize the different curves, where
%$\tan\theta_c = \frac{b}{a}$,  $b$ and $a$ are the typical parameters of conics. A positive value for $\theta_c$ indicates that the given curve is a closed one, i.e
%an ellipse, while a negative value indicates that is an hyperbola. %Insert figures if neccesary  
\begin{figure}
\setlength\tabcolsep{0pt}
\begin{tabular}{cc}
\includegraphics[height=0.54\linewidth, trim=30 0 30 0, clip]{ellipse_py} &
\includegraphics[height=0.54\linewidth, trim=60 0 70 0, clip]{hyperbola_py}
\end{tabular}
\label{fig:conics}
\caption{Schematic representation of conic like bowshocks: A) Ellipse and B) Hyperbola.
  The center of the conic is located at a distance $x_0=R_0-a$ from the origin at the $x$ axis 
  The radius of curvature at the axis is $R_c$, and $R_{90}$ is t he radius of the conic in the
  perpendicular direction to $R_0$.
}
\end{figure}
\begin{figure}
\includegraphics[width=\linewidth]{conic1}
\caption{Example of a family of conic sections, all with the same
  radius of curvature at their apex (marked by white dot) on the
  \(x\)~axis: \(R_c = 2 R_0\). The parameter
  $\theta_c = \pm \tan^{-1} b/a$ describes the family, with negative
  values corresponding to hyperbolae.}
\label{fig:conics-family}
\end{figure}

@@

With  $f(i;\theta_c)\equiv\left(1\pm\tan^2\theta_c\tan^2i\right)^{1/2}$ we find that:
\begin{align}
\frac{R'_0}{D'}=\frac{R_0}{D}\left(1\pm A\cot^2\theta_c(f(i;\theta_c)-1) \right)
\end{align}
%Where $A\equiv \frac{R_c}{R_0}$

The Radius of curvature in the observer's frame is given by $R'_c=\frac{b'^2}{a'}$. Then:
\begin{align}
\frac{R'_c}{R'_0} = \frac{A}{\cos^2 i f(i;\theta_c)\frac{q'}{q}}
\end{align}
where $q=\frac{R_0}{D}$ and $q' = \frac{R'_0}{D'}$. 
% \begin{figure*}
% \includegraphics[width=0.8\linewidth]{conic2}
% \label{fig:conic2}
% \caption{Graphic example of the increasing of the projected radius of curvature with inclination}
% \end{figure*}

@@

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "proplyd-bowshocks"
%%% End:

>>>>

%Instead of the excentricity, we utilize the parameter $\theta_c$ to characterize the different curves, where
%$\tan\theta_c = \frac{b}{a}$,  $b$ and $a$ are the typical parameters of conics. A positive value for $\theta_c$ indicates that the given curve is a closed one, i.e
%an ellipse, while a negative value indicates that is an hyperbola. %Insert figures if neccesary  
\begin{figure*}
\setlength\tabcolsep{0pt}
\begin{tabular}{ll}
  (a) & (b) \\
  \includegraphics[height=0.45\linewidth]{figs/ellipse_py}
      & \includegraphics[height=0.45\linewidth]{figs/hyperbola_py}
\end{tabular}
\label{fig:conics}
\caption{Example off-center conic sections that can form quadrics of
  revolution: (a) ellipse, (b) hyperbola.  The relationship is shown
  between the conic section parameters \(a\), \(b\), \(\theta_c\) and
  the bowshock characteristic radii \(R_0\), \(R_{90}\), \(R_c\), as
  defined in Fig.~\ref{fig:characteristic-radii}. The center of the
  conic is located at a distance $x_0=R_0-a$ from the origin along the
  $x$ axis.  }
\end{figure*}
\begin{figure}
\includegraphics[width=\linewidth]{conic1}
\caption{Example of a family of conic sections, all with the same
  radius of curvature at their apex (marked by white dot) on the
  \(x\)~axis: \(R_c = 2 R_0\). The parameter
  $\theta_c = \pm \tan^{-1} b/a$ describes the family, with negative
  values corresponding to hyperbolae.}
\label{fig:conics-family}
\end{figure}

@@

With  $f(i;\theta_c)\equiv\left(1\pm\tan^2\theta_c\tan^2i\right)^{1/2}$ we find that:
\begin{align}
\frac{R'_0}{D'}=\frac{R_0}{D}\left(1\pm A\cot^2\theta_c(f(i;\theta_c)-1) \right)
\label{eq:qprime}
\end{align}
%Where $A\equiv \frac{R_c}{R_0}$

The Radius of curvature in the observer's frame is given by $R'_c=\frac{b'^2}{a'}$. Then:
\begin{align}
  \frac{R'_c}{R'_0} = \frac{A}{\cos^2 i f(i;\theta_c)\frac{q'}{q}}
  \label{eq:Aprime}
\end{align}
where $q=\frac{R_0}{D}$ and $q' = \frac{R'_0}{D'}$. 
% \begin{figure*}
% \includegraphics[width=0.8\linewidth]{conic2}
% \label{fig:conic2}
% \caption{Graphic example of the increasing of the projected radius of curvature with inclination}
% \end{figure*}

@@

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "quadrics-bowshock"
%%% End:
